\section{Bibliografia}

\begin{thebibliography}{30} 

\bibitem{po} http://www.scrumalliance.org/articles/44-being-an-effective-product-owner
\bibitem{scrum} Ken Schwaber (2004). \textit{Agile Project Management with Scrum}. Microsoft Press.
\bibitem{xp} Kent Beck (2004). \textit{Extreme Programming Explained}. Addison-Wesley; 2nd edition
\bibitem{kanban} http://www.infoq.com/articles/agile-kanban-boards
\bibitem{brooks} Frederich Brooks (2010). \textit{Design of Design}. Addison-Wesley Professional; 1st edition
\bibitem{manifesto} Kent Beck, Alistair Cockburn, Martin Fowler, et al. \textit{Agile Manifesto}. http://www.agilemanifesto.org;
\bibitem{waterfall} Winston W Royce (1970). \textit{Managing the development of large software systems}.
Proceedings of IEEE Wescon, 1970;
\bibitem{rup} Rational Software Corporation (2000). \textit{Rational Unified Process -- Best Practices for Software Development Teams}. White paper;
\bibitem{change} Laurie Williams, Alistair Cockburn (June, 2003) \textit{Guest Editors' Introduction: Agile Software Development: It's about Feedback and Change}. Computer, vol. 36, no. 6, pp. 39-43;
\bibitem{pair} Laurie Williams, Alistais Cockburn (2001). \textit{The costs and benefits of pair programming}. Extreme programming examined, 2001 - Citeseer;
\bibitem{refactoring} Martin Fowler, Kent Beck, et al (1999). \textit{Refactoring: Improving the Design of Existing Code}; 1st edition;
\bibitem{ci} http://martinfowler.com/articles/continuousIntegration.html(2006)
\bibitem{dsl} http://martinfowler.com/bliki/DomainSpecificLanguage.html (2006)
\bibitem{di} http://www.informit.com/articles/article.aspx?p=1404056 (2009)
\bibitem{fowler} Martin Fowler (2002). \textit{Patterns of Enterprise Application Architecture}.  Addison-Wesley Longman Publishing Co., Inc.
\bibitem{dao} http://java.sun.com/blueprints/corej2eepatterns/Patterns/DataAccessObject.html
\bibitem{rest} Leonard Richardson, Sam Ruby (2007). \textit{RESTful Web Services}. O'Reilly
\bibitem{gof} Erich Gamma, Richard Helm, Ralph Johnson, John Vlissides (1995). \textit{Design Patterns: Elements of reusable object-oriented software}. Addison-Wesley, 1st edition
\bibitem{effective} Joshua Bloch (2008). \textit{Effective Java}. Addison-Wesley; 2nd edition
\bibitem{rest-jim} http://jim.webber.name/downloads/presentations/2009-05-HATEOAS.pdf
\bibitem{ddd} Eric Evans (2004). \textit{Domain Driven Design}. Addison-Wesley; 1st edition 
\bibitem{rest-roy} Roy Fielding (2000). \textit{Architectural Styles and the Design of Network-based Software Architectures}. http://www.ics.uci.edu/~fielding/pubs/dissertation/top.htm
\bibitem{rest-infoq} http://www.infoq.com/articles/rest-introduction
\bibitem{mimetypes} http://www.iana.org/assignments/media-types/
\bibitem{bdd} Dan North (2006). http://dannorth.net/introducing-bdd

\end{thebibliography}
